Causes and effects in Dichotomous Comparative Judgments: an information-theoretical system of plausible mechanism

### 2024-08-06 _tex/index.tex
Built site for gh-pages

DAGs offer two key advantages for modeling causality. Firstly, DAGs
represent causal relations in a nonparametric and fully interactive
manner. This feature implies that feasible causal analysis strategies
usually do not require specifying the type of data or the nature of the
functional dependence among variables \citep{Morgan_et_al_2014}.
Secondly, regardless of complexity, DAGs can represent various causal
structures using only five fundamental building blocks
\citep{Neal_2020, McElreath_2020}. These building blocks can be depicted
in three ways: the magnified representation, the standard
representation, and the structural causal model form
\citep[SCM,][]{Morgan_et_al_2014}.

>>>>

DAGs offer two key advantages for modeling causality. Firstly, DAGs
represent causal relations in a nonparametric and fully interactive
manner. This feature implies that feasible causal analysis strategies
usually do not require specifying the type of data or the nature of the
functional dependence among variables \citep{Morgan_et_al_2014}.
Secondly, regardless of complexity, DAGs can represent various causal
structures using only five fundamental building blocks
\citep{Neal_2020, McElreath_2020}. This further implies that to
understand the causal assumptions of a complex system, one can decompose
a structure into these basic building blocks and analyze the causal
assumptions associated with each block individually
\citep{McElreath_2020}. Importantly, these building blocks can be
represented in three ways: the magnified representation, the standard
representation, and the structural causal model form
\citep[SCM,][]{Morgan_et_al_2014}.
